Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2021-11-18 doc/JFLA2022/paper.tex
macro for coq_makefile

\newcommand{\TODO}[2][]{[\textcolor{red}{TODO (#1):} \emph{#2}]}
\newcommand{\coq}{Coq\xspace}
\newcommand{\coqdoc}{Coqdoc\xspace}
\newcommand{\community}{Coq-community\xspace}
\newcommand{\gaia}{Gaia\xspace}
\newcommand{\alectr}{Alectryon\xspace}
\newcommand{\equations}{Equations\xspace}
\newcommand{\Hydras}{Hydras \& Co$\text.$\xspace}
%\newcommand{\Hydras}{Hydra-battles\xspace}

@@

In practice, we do still support building the whole project with coq\_makefile, and we actually rely on this build system in our documentation generation pipeline.

@@

\begin{enumerate}
\item To test the build of the project (as a single unit) with coq\_makefile (whereas the Docker-based CI relies on the opam packages, which use Dune to build the libraries contained in the project).

\item To generate the documentation of the project (book in PDF format and \coqdoc HTML pages) by relying on the output of the coq\_makefile build.

>>>>

\newcommand{\TODO}[2][]{[\textcolor{red}{TODO (#1):} \emph{#2}]}
\newcommand{\coq}{Coq\xspace}
\newcommand{\coqdoc}{Coqdoc\xspace}
\newcommand{\coqmakefile}{coq\_makefile\xspace}
\newcommand{\community}{Coq-community\xspace}
\newcommand{\gaia}{Gaia\xspace}
\newcommand{\alectr}{Alectryon\xspace}
\newcommand{\equations}{Equations\xspace}
\newcommand{\Hydras}{Hydras \& Co$\text.$\xspace}
%\newcommand{\Hydras}{Hydra-battles\xspace}

@@

In practice, we do still support building the whole project with \coqmakefile, and we actually rely on this build system in our documentation generation pipeline.

@@

\begin{enumerate}
\item To test the build of the project (as a single unit) with \coqmakefile (whereas the Docker-based CI relies on the opam packages, which use Dune to build the libraries contained in the project).

\item To generate the documentation of the project (book in PDF format and \coqdoc HTML pages) by relying on the output of the \coqmakefile build.
